Supplementary Materials - Needle in a haystack, the pollen dataset

### 2020-09-16 supp-mouse.Rmd
reformat supplementary material, add materials as zip file

---
title: "Supplementary Materials"
output: html_document
date: "`r Sys.Date()`"
---

@@

# Intro

Here we provide side by side view of animations provided in the case studies of our paper:

>  Burning sage: Reversing the curse of dimensionality in the visualisation of high-dimensional data

The left hand side is always the grand tour, and the right is the sage tour.

@@

Setting sage with $\gamma = 3$

@@

## QuickDraw Sketches

<img src="gifs/sketches_grand.gif" width="450"/> <img src="gifs/sketches_sage.gif" width="450"/>

## pdfsense

Setting sage tour with $R = 10$.

<img src="gifs/pdfsense_grand.gif" width="450"/> <img src="gifs/pdfsense_sage_r10.gif" width="450"/>

## pollen: parameter tuning

All sage displays: left is default, middle is $R=1$, and right is $\gamma=20$.

<img src="gifs/pollen_sage.gif" width="300"/> <img src="gifs/pollen_sage_R1.gif" width="300"/> <img src="gifs/pollen_sage_gam20.gif" width="300"/>

>>>>

---
title: "Supplementary Materials - Single Cell Mouse Retina Data"
output: html_document
date: "`r Sys.Date()`"
---

@@

@@

The left hand side is the regular tour
display, and the right hand side is sage display with $\gamma = 3$.

@@

### 2020-09-16 supp-pollen.Rmd
reformat supplementary material, add materials as zip file

---
title: "Supplementary Materials"
output: html_document
date: "`r Sys.Date()`"
---

@@

# Intro

Here we provide side by side view of animations provided in the case studies of our paper:

>  Burning sage: Reversing the curse of dimensionality in the visualisation of high-dimensional data

The left hand side is always the grand tour, and the right is the sage tour.

##  Single cell RNA-seq data from mouse retina

Setting sage with $\gamma = 3$

<img src="gifs/mouse_grand_2c.gif" width="450"/> <img src="gifs/mouse_sage_2c_gam3.gif" width="450"/>

## QuickDraw Sketches

<img src="gifs/sketches_grand.gif" width="450"/> <img src="gifs/sketches_sage.gif" width="450"/>

## pdfsense

Setting sage tour with $R = 10$.

<img src="gifs/pdfsense_grand.gif" width="450"/> <img src="gifs/pdfsense_sage_r10.gif" width="450"/>

>>>>

---
title: "Supplementary Materials - Needle in a haystack, the pollen dataset"
output: html_document
date: "`r Sys.Date()`"
---

@@
